Kelompok 4_Praktikum_Pekan 8

### 2024-04-07 Project/Kelompok 4_Praktikum_Pekan 8.Rmd
Update

```{r}
set.seed(361)
sample_size <- c(2, 5, 25)

@@

print(norm_samples)
```

@@

```{r}
set.seed(361)
unif_samples <- lapply(sample_size, function(n) runif(n))

print(unif_samples)
```

@@

```{r}
set.seed(361)
exp_samples <- lapply(sample_size, function(n) rexp(n))

print(exp_samples)
```

>>>>

```{r fig.height=3.5, fig.width=10, dpi=300}
set.seed(58)
sample_size <- c(2, 5, 25)

@@

print(norm_samples)

par(mfrow = c(1, 3))
hist(norm_samples[[1]], main = "Histogram Normal n=2", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#d9eacb")
hist(norm_samples[[2]], main = "Histogram Normal n=5", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#b4e69e")
hist(norm_samples[[3]], main = "Histogram Normal n=25", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#8DC16D")
```

@@

```{r fig.height=3.5, fig.width=10, dpi=300}
set.seed(22)
unif_samples <- lapply(sample_size, function(n) runif(n))

print(unif_samples)

par(mfrow = c(1, 3))
hist(unif_samples[[1]], main = "Histogram Seragam n=2", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#c8daf0")
hist(unif_samples[[2]], main = "Histogram Seragam n=5", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#a2c6eb")
hist(unif_samples[[3]], main = "Histogram Seragam n=25", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#4493CA")
```

@@

```{r fig.height=3.5, fig.width=10, dpi=300}
set.seed(88)
exp_samples <- lapply(sample_size, function(n) rexp(n))

print(exp_samples)

par(mfrow = c(1, 3))
hist(exp_samples[[1]], main = "Histogram Eksponensial n=2", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#E4B3BA")
hist(exp_samples[[2]], main = "Histogram Eksponensial n=5", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#DE7C8A")
hist(exp_samples[[3]], main = "Histogram Eksponensial n=25", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#D44155")
```
